Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-07-25 paper-correlations.tex
Add missing citation
Change document class

\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs,nofootinbib]{revtex4-1}
% Latex
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% Xelatex
%\usepackage{polyglossia}
%\usepackage{fontspec}
%\setdefaultlanguage{english}
%\setmainfont{DejaVu Sans}
%\setsansfont{DejaVu Sans}
%\setmonofont{DejaVu Sans Mono}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[export]{adjustbox}

@@

\begin{document}
\preprint{APS/123-QED}

\author{Vasily Postnicov\textsuperscript{1}}
\author{Aleksei Samarin\textsuperscript{1,2}}
\author{Marina Karsanina\textsuperscript{1}}
\author{Aleksey Khlyupin\textsuperscript{1}}
\author{Kirill Gerke\textsuperscript{1}}
\email{kg@ifz.ru}

\affiliation{\textsuperscript{1}Schmidt Institute of Physics of the Earth of
  Russian Academy of Sciences, Moscow, 107031, Russia}
\affiliation{\textsuperscript{2}Computational Mathematics and Cybernetics,
  Lomonosov Moscow State University, Moscow, 119991, Russia}

@@

Our library does not have an implementation for lineal-path maps, although we
know that such implementations exist \cite{Paper}. The reason is a very slow
computation even on GPUs, plus the resulting map is not for all points on the
image, but within a spherical volume (due to rotation of the 3D image during
lineal-path evaluation). Moreover, linear scan approach is orders of magnitude
faster for $L_2$.

@@

\begin{table*}[!pt]
  \centering
  \begin{ruledtabular}
    \begin{tabular}{|c|c|c|c|c|}
      Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
      \hline
      Ceramic 1   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9823 \\
      Ceramic 2   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9890 \\
      Ceramic 3   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9712 \\
      Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
      Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 & 0.9897 \\
      Carbonate 1 & SEM &  $1024 \times 691$ & 0.06 & 0.9721
    \end{tabular}
  \end{ruledtabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:samples}
\end{table*}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.6\linewidth]{images/timing-image.png}
  \caption[]{One of 2D image used in timing measurements.}
  \label{fig:valuenoise}
\end{figure}

>>>>

\documentclass[1p]{elsarticle}
% Latex
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% Xelatex
%\usepackage{polyglossia}
%\usepackage{fontspec}
%\setdefaultlanguage{english}
%\setmainfont{DejaVu Sans}
%\setsansfont{DejaVu Sans}
%\setmonofont{DejaVu Sans Mono}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[export]{adjustbox}

@@

\bibliographystyle{elsarticle-num}
\journal{Physica A: Statistical Mechanics and its Applications}

\begin{document}

\author[Smith]{Vasily~Postnicov}
\author[Smith,MIT]{Aleksei~Samarin}
\author[Smith]{Marina~Karsanina}
\author[Smith]{Aleksey~Khlyupin}
\author[Smith]{Kirill~Gerke}
\ead{kg@ifz.ru}

\address[Smith]{Schmidt Institute of Physics of the Earth of Russian Academy of
  Sciences, Moscow, 107031, Russia}
\address[MIT]{Computational Mathematics and Cybernetics, Lomonosov Moscow State
  University, Moscow, 119991, Russia}

@@

Our library does not have an implementation for lineal-path maps, although we
know that such implementations exist \cite{havelkafast}. The reason is a very
slow computation even on GPUs, plus the resulting map is not for all points on
the image, but within a spherical volume (due to rotation of the 3D image during
lineal-path evaluation). Moreover, linear scan approach is orders of magnitude
faster for $L_2$.

@@

\begin{table}[!pt]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Ceramic 1   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9823 \\
    Ceramic 2   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9890 \\
    Ceramic 3   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9712 \\
    Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 & 0.9897 \\
    Carbonate 1 & SEM &  $1024 \times 691$ & 0.06 & 0.9721 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:samples}
\end{table}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.45\linewidth]{images/timing-image.png}
  \caption[]{One of 2D image used in timing measurements.}
  \label{fig:valuenoise}
\end{figure}
